ins---
title: "Milk Analysis"
author: "Gustavo Reyes"
date: "10/25/2021"
output: html_document
---
#Milk Analysis: 

```{r}
#Setting Working Directory-------------------------------------
setwd(dirname(rstudioapi::getActiveDocumentContext()$path)) #Set working directory to the path of document
```

## Loading Libraries
```{r ,echo=FALSE warning=FALSE}
#Opening Libary and Inputs-------------------------------------
source("Util_Library.R")
source("Functions_Full_Analysis.R")
```

## Loading Model Necessary Inputs. 
```{r, include=FALSE}
library(tidyverse)
#Inputs and Source Files-------------------------------------
#Inputs
source("Main_Loop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_Output_Functions.R")
```

## Functions for growth and lag phases 
```{r}
#Function for growth and lag phase
#Note for Lmo changed the minimum growth temp (T0) to uniform distribution taken from Ramos et al 2023, Koutsoumanis et al. 2010 use Normal (−2.47, 1.26) for T0, which is another option
#Old temp is the 5C reference temp # distribution from Ramos T0 = runif(1,-2,-1), we use -2 here as worst case
new_growth_rate<-function(newTemp, oldMu,oldTemp = 5, T0 = -2){
  newMu<-(((newTemp-T0)/(oldTemp-T0))^2)* oldMu #in alignment with WHO FAO 2004 & Ramos et al 2023 equation, note change to square the value of the first term of the equation
  return (newMu)
}

#Calculation of the new lag time.
new_lag_time <- function (newTemp, oldLag, oldTemp = 5, T0 = -2) {
  numerator <- oldTemp -T0
  denom <- newTemp - T0
  newLag <- ( (numerator / denom)^2) * oldLag
  return(newLag)
}
```

#Function for lag models and buchanan three-phrase model
```{r}
#This function calculates thee growth based on a time and temperature profile for 1 specific milk with Listeria monocytogenes 
Func_Growth_LagCon<-function(In_Lag_Consumed, Time_Temp_df,Interval, AF){
  #In_Lag_Consumed= Total lag time consumed
  #Time_Temp_df = dataframe with time and temperature conditions
  #Interval = time interval in the time_temp_df in hrs. 
  Total_Lag_Consumed = In_Lag_Consumed
  Total_Growth = 0
  old_lag = 0 #for now assuming no lag
  NMax = 8.5 #came from Koutsoumanis et al. 2010
  old_mumax = 0.0181 #runif(1, 0.00383, 0.0181) #converted WHO FAO 2004 value for Lm growth at 5C in milk
  Growth_V = c()
  for (i in 1:nrow(Time_Temp_df)){
    if (Total_Lag_Consumed <1 && old_lag!=0){
      Lag_t_interval<-new_lag_time(newTemp = Time_Temp_df$MilkTemp[i], oldLag = old_lag)
      Lag_Consumed<-Interval/Lag_t_interval
      Total_Lag_Consumed<-Total_Lag_Consumed+Lag_Consumed
      Growth = 0
    } else if (Total_Lag_Consumed>=1 | old_lag == 0){
      Growth = ((new_growth_rate(newTemp = Time_Temp_df$MilkTemp[i], oldMu = old_mumax))*AF)
      Total_Growth = Total_Growth + (Growth*Interval)
    }
    Growth_V = c(Growth_V,Total_Growth)
    #print(length(Growth_V))
  }
  return(list(Total_Growth,Total_Lag_Consumed,Growth_V))
}

#Buchanan three phrase function
LMO_Function_Single_Milk<-function(Cont, Pop_Max, Time_Temp_df, Interval =1/60, AF){
  Lag_Consumed = 0
  #this function provides two outputs, the total growth, and the new updated lag phase consumed. 
  Output_Milk<-Func_Growth_LagCon(In_Lag_Consumed = Lag_Consumed ,Time_Temp_df = Time_Temp_df,Interval = Interval, AF=AF)
  Lag_Consumed = Output_Milk[[2]]
  Cont<-Output_Milk[[1]]+Cont
  if( Cont>Pop_Max){
     Cont = Pop_Max
  }
  return (list(Cont,Output_Milk[[3]]))
}
```

#Function to apply growth model in milk based on time and temperature profile
```{r}
#Applying Changes over time with N max limit
Appling_Changes<-function(df,Changes_Over_Time){
  NMax = 8.5 #updated 
  Contamination_v<-df$InLMOCon
  Time_V<-df$TotTime
  Final_contamination_v<-c()
  for (i in 1:nrow(df)){
    In_Cont<-Contamination_v[i]
    Time<-Time_V[i]
    if (Time == 0){
      Total_Growth = 0
    }else{
      Total_Growth<-Changes_Over_Time[Time]
    }
    Final_Con<-In_Cont+Total_Growth
    if(Final_Con>NMax){
      Final_Con <- NMax
    }
    Final_contamination_v<-c(Final_contamination_v,Final_Con)
  }
  df$LMOCon<-Final_contamination_v
  return(df)
}
```


#Importing time and Temp Profiles. 
```{r}
#Before Running this make sure that the files from "Time and Temperature Profiles.rmd" have been generated accordingly

## Primary Scenarios
#Room Temp B
Df_RT_MT_RTB<-read.csv("Pedicted Time and Temp Profiles/Df_RT_MT_RTB.csv") 
#Refrigerated Tray
Df_RT_MT_RT<-read.csv("Pedicted Time and Temp Profiles/Df_RT_MT_RT.csv") 
#Tray With Ice Packs
Df_RT_MT_TIP<-read.csv("Pedicted Time and Temp Profiles/Df_RT_MT_TIP.csv") 
#Tray with Ice 
Df_RT_MT_TIC<-read.csv("Pedicted Time and Temp Profiles/Df_RT_MT_TIC.csv") 
#Cooler with Ice
Df_RT_MT_CI<-read.csv("Pedicted Time and Temp Profiles/Df_RT_MT_CI.csv")
#room temp b with ref break
Df_RT_MT_RTB_refB<-read.csv("Pedicted Time and Temp Profiles/Df_RT_MT_RTB_refB.csv")

## Temperature Scenarios
#Room Temp B
Df_RT_MT_RTB_18C<-read.csv("Pedicted Time and Temp Profiles/Df_RT_MT_RTB_18C.csv") 
#Refrigerated Tray
Df_RT_MT_RTB_21C<-read.csv("Pedicted Time and Temp Profiles/Df_RT_MT_RTB_21C.csv") 
#Tray With Ice Packs
Df_RT_MT_RTB_23C<-read.csv("Pedicted Time and Temp Profiles/Df_RT_MT_RTB_23C.csv") 

## Updated Refrigeration Temps
#At 7 C
Df_RT_MT_Ref_7C<-read.csv("Pedicted Time and Temp Profiles/Df_RT_MT_Ref_7C.csv") 
#At 2 C 
Df_RT_MT_Ref_2C<-read.csv("Pedicted Time and Temp Profiles/Df_RT_MT_Ref_2C.csv")
#At 4 C 
Df_RT_MT_Ref_4C<-read.csv("Pedicted Time and Temp Profiles/Df_RT_MT_Ref_4C.csv")


#Bell Schedule Scenarios
#Very long
Df_RT_MT_s5b4<-read.csv("Pedicted Time and Temp Profiles/Df_RT_MT_s5b4.csv")
#Long
Df_RT_MT_s4b3<-read.csv("Pedicted Time and Temp Profiles/Df_RT_MT_s4b3.csv")
#Very short
Df_RT_MT_s1b0<-read.csv("Pedicted Time and Temp Profiles/Df_RT_MT_s1b0.csv")
#Short
Df_RT_MT_s2b1<-read.csv("Pedicted Time and Temp Profiles/Df_RT_MT_s2b1.csv")
#Medium
Df_RT_MT_s3b2<-read.csv("Pedicted Time and Temp Profiles/Df_RT_MT_s3b2.csv")
#Long + Tray with Ice 
Df_RT_MT_s4b3TIC<-read.csv("Pedicted Time and Temp Profiles/Df_RT_MT_s4b3TIC.csv")
#Long + Tray with Ice Packs
Df_RT_MT_s4b3TIP<-read.csv("Pedicted Time and Temp Profiles/Df_RT_MT_s4b3TIP.csv")
#Very long + Tray with Ice 
Df_RT_MT_s5b4TIC<-read.csv("Pedicted Time and Temp Profiles/Df_RT_MT_s5b4TIC.csv")
#very long + Tray with Ice Packs
Df_RT_MT_s5b4TIP<-read.csv("Pedicted Time and Temp Profiles/Df_RT_MT_s5b4TIP.csv")

#high contamination level
Df_RT_MT_highcon<-read.csv("Pedicted Time and Temp Profiles/Df_RT_MT_RTB.csv")
```


##Running the  Model for Milk.

If conditions are changed, need to change in the input_static, Service Outputs, Days Outputs files.

- To change the number of weeks: Input_Static : Sens_Iterations
- To change the number of Days, Services: Input_Static : Days_No, Service_No
- To Change the Service Time: Input Static: Time_Service_Length
- To change the In between Input Static: Time_Turnaround_Length
- To Change the Overnight Storage time: Input Static: Time_Overnight_Length
- To Change the contamination levels: Input Static: Milk_Con_Mean, and Milk_Con_SD

The simulation below will generate all the milks throughout the 37*50 weeks for baseline length of service. 
Then we will run the simulation with input_static that toggles the ST off and 5 different lengths of services. 

```{r warning=TRUE}
#This chunk Runs the ST Model 
Obtaining_LMO_Milks_DFs<-function(N_Years, Service_Length,TurningT_Length){
  final_list <- list()
  #Define the length of periods to match your model to properly adjust time. 
  Service_Length = Service_Length#50
  TurningT_Length = TurningT_Length#25
  
  for (i in 1:N_Years){
    print(i)
    start_time<-Sys.time()
    source("Main_Loops2.R")
    
    #1. Start from here
    Individual_Analysis_Milk<-rbind.fill(List_Sens_Pre)
    
    #2. find the duplicates
    
    #this step filters replicated based on the ID
    Individual_Analysis_Milk<-Individual_Analysis_Milk %>% 
      group_by(ID) %>% 
      filter(TotServices==max(TotServices))
    
    #3. Add time to the system
    AnalysysDF<-Individual_Analysis_Milk
    #Adding the time of the services for those milks that were added to the service line during the lunch period.
    AnalysysDF[AnalysysDF$Initial.Service>1,]
    AnalysysDF$TotTime<-AnalysysDF$TotTime+(as.integer(AnalysysDF$Initial.Service)-1)*(Service_Length+TurningT_Length)
    
    AnalysysDF$Shared<-ifelse(AnalysysDF$STtimes>0, "Yes", "No")
    
    final_list<-append(final_list,list(AnalysysDF))
    end_time<-Sys.time()
  
    Total_time<-end_time-start_time
    print(Total_time)
  }
  return(final_list)
}
```


### When running up to this point
```{r warning=TRUE}

#normal service, changes in time and temp profile #this runs the model
source("Input_Static.R")
Outs_DFs<-Obtaining_LMO_Milks_DFs(N_Years = 50, Service_Length = 50,TurningT_Length = 25) 

Outs_DFs_RTB<-Outs_DFs
Outs_DFs_RT<-Outs_DFs
Outs_DFs_TIP<-Outs_DFs
Outs_DFs_TIC<-Outs_DFs
Outs_DFs_CI<-Outs_DFs
Outs_DFs_RTB_refB<-Outs_DFs
Outs_DFs_RTB_18C<-Outs_DFs
Outs_DFs_RTB_21C<-Outs_DFs
Outs_DFs_RTB_23C<-Outs_DFs
Outs_DFs_Ref_7C<-Outs_DFs
Outs_DFs_Ref_2C<-Outs_DFs
Outs_DFs_Ref_4C<-Outs_DFs
```

#ST off model run 
```{r warning=TRUE}

source("Input_Static_stoff.R")
Outs_DFs_SToff<-Obtaining_LMO_Milks_DFs(N_Years = 50, Service_Length = 50,TurningT_Length = 25)
```


# Difference Services model run
```{r warning=TRUE}
#Difference Services
source("Input_Static_s1b0.R")
Outs_DFs_1sb0<-Obtaining_LMO_Milks_DFs(N_Years = 50, Service_Length = 40,TurningT_Length = 0)

source("Input_Static_s2b1.R")
Outs_DFs_2sb1<-Obtaining_LMO_Milks_DFs(N_Years = 50, Service_Length = 30,TurningT_Length = 14)

source("Input_Static_s3b2.R")
Outs_DFs_3sb2<-Obtaining_LMO_Milks_DFs(N_Years = 50, Service_Length = 31,TurningT_Length = 16)

source("Input_Static_s4b3.R")
Outs_DFs_4s3b<-Obtaining_LMO_Milks_DFs(N_Years = 50, Service_Length = 50,TurningT_Length = 7)

source("Input_Static_s5b4.R") 
Outs_DFs_5s4b<-Obtaining_LMO_Milks_DFs(N_Years = 50, Service_Length = 50,TurningT_Length = 4)

#Longer Bell Schedules Plus Storage Systems 
source("Input_Static_s4b3.R")
Outs_DFs_4sb3TIC<-Outs_DFs_4s3b

source("Input_Static_s4b3.R")
Outs_DFs_4sb3TIP<-Outs_DFs_4s3b

source("Input_Static_s5b4.R")
Outs_DFs_5sb4TIC<-Outs_DFs_5s4b

source("Input_Static_s5b4.R")
Outs_DFs_5sb4TIP<-Outs_DFs_5s4b

# High contamination 
source("Input_Static_highcon.R")
Outs_DFs_highcon<-Obtaining_LMO_Milks_DFs(N_Years = 50, Service_Length = 50,TurningT_Length = 25) 
```


# Generate the conbimed dataset (50 years in one dataframe) for each condition. 
#Baseline service, Storage Conditions
##RTB
```{r}
RTB_List<-list()  
Output_Milk_RTB<-LMO_Function_Single_Milk(Cont = 0, Pop_Max =8.5, Time_Temp_df = Df_RT_MT_RTB, Interval =1/60,AF = 1)
Changes_Over_Time_RTB<-Output_Milk_RTB[[2]]

for (i in 1:50){
  AnalysysDF_RTB<- Appling_Changes(df = Outs_DFs_RTB[[i]], Changes_Over_Time = Changes_Over_Time_RTB)
  RTB_List<-append(RTB_List,list(AnalysysDF_RTB))
}

RTB_List[[i]]

RTB_Combined <- bind_rows(RTB_List)

```


##High contamination
```{r}
RTB_highcon_List<-list()  
Output_Milk_RTB_highcon<-LMO_Function_Single_Milk(Cont = 0, Pop_Max =8.5, Time_Temp_df = Df_RT_MT_highcon, Interval =1/60,AF = 1)
Changes_Over_Time_RTB_highcon<-Output_Milk_RTB_highcon[[2]]

for (i in 1:50){
  AnalysysDF_RTB_highcon<- Appling_Changes(df = Outs_DFs_highcon[[i]], Changes_Over_Time = Changes_Over_Time_RTB_highcon)
  RTB_highcon_List<-append(RTB_highcon_List,list(AnalysysDF_RTB_highcon))
}

RTB_highcon_List[[i]]

RTB_highcon_Combined <- bind_rows(RTB_highcon_List)

```


##RTR
```{r}
RT_List<-list()  
Output_Milk_RT<-LMO_Function_Single_Milk(Cont = 0, Pop_Max =8.5, Time_Temp_df = Df_RT_MT_RT, Interval =1/60,AF = 1)
Changes_Over_Time_RT<-Output_Milk_RT[[2]]
for (i in 1:50){
  AnalysysDF_RT<- Appling_Changes(df = Outs_DFs_RT[[i]], Changes_Over_Time = Changes_Over_Time_RT)
  RT_List<-append(RT_List,list(AnalysysDF_RT))
}


RT_List[[i]]

RT_Combined <- bind_rows(RT_List)

```


##TIP
```{r}
TIP_List<-list()  
Output_Milk_TIP<-LMO_Function_Single_Milk(Cont = 0, Pop_Max =8.5, Time_Temp_df = Df_RT_MT_TIP, Interval =1/60,AF = 1)
Changes_Over_Time_TIP<-Output_Milk_TIP[[2]]
for (i in 1:50){
  AnalysysDF_TIP<- Appling_Changes(df = Outs_DFs_TIP[[i]], Changes_Over_Time = Changes_Over_Time_TIP)
  TIP_List<-append(TIP_List,list(AnalysysDF_TIP))
}

TIP_List[[i]]

TIP_Combined <- bind_rows(TIP_List)
```



##TIC
```{r}
TIC_List<-list()  
Output_Milk_TIC<-LMO_Function_Single_Milk(Cont = 0, Pop_Max =8.5, Time_Temp_df = Df_RT_MT_TIC, Interval =1/60,AF = 1)
Changes_Over_Time_TIC<-Output_Milk_TIC[[2]]
for (i in 1:50){
  AnalysysDF_TIC<- Appling_Changes(df = Outs_DFs_TIC[[i]], Changes_Over_Time = Changes_Over_Time_TIC)
  TIC_List<-append(TIC_List,list(AnalysysDF_TIC))
}

TIC_List[[i]]

TIC_Combined <- bind_rows(TIC_List)

```


##CI
```{r}
CI_List<-list()  
Output_Milk_CI<-LMO_Function_Single_Milk(Cont = 0, Pop_Max =8.5, Time_Temp_df = Df_RT_MT_CI, Interval =1/60,AF = 1)
Changes_Over_Time_CI<-Output_Milk_CI[[2]]
for (i in 1:50){
  AnalysysDF_CI<- Appling_Changes(df = Outs_DFs_CI[[i]], Changes_Over_Time = Changes_Over_Time_CI)
  CI_List<-append(CI_List,list(AnalysysDF_CI))
}

CI_List[[i]]

CI_Combined <- bind_rows(CI_List)
```



##RTB_refB
```{r}
RTB_refB_List<-list()  
Output_Milk_RTB_refB<-LMO_Function_Single_Milk(Cont = 0, Pop_Max =8.5, Time_Temp_df = Df_RT_MT_RTB_refB, Interval =1/60,AF = 1)
Changes_Over_Time_RTB_refB<-Output_Milk_RTB_refB[[2]]
for (i in 1:50){
  AnalysysDF_RTB_refB<- Appling_Changes(df = Outs_DFs_RTB_refB[[i]], Changes_Over_Time = Changes_Over_Time_RTB_refB)
  RTB_refB_List<-append(RTB_refB_List,list(AnalysysDF_RTB_refB))
}

RTB_refB_List[[i]]

RTB_refB_Combined <- bind_rows(RTB_refB_List)
```


#Room Temperature Conditions
##18C
```{r}
RTB_18C_List<-list()  
Output_Milk_RTB_18C<-LMO_Function_Single_Milk(Cont = 0, Pop_Max =8.5, Time_Temp_df = Df_RT_MT_RTB_18C, Interval =1/60,AF = 1)
Changes_Over_Time_RTB_18C<-Output_Milk_RTB_18C[[2]]
for (i in 1:50){
  AnalysysDF_RTB_18C<- Appling_Changes(df = Outs_DFs_RTB_18C[[i]], Changes_Over_Time = Changes_Over_Time_RTB_18C)
  RTB_18C_List<-append(RTB_18C_List,list(AnalysysDF_RTB_18C))
}

RTB_18C_List[[i]]

RTB_18C_Combined <- bind_rows(RTB_18C_List)
```




##21C
```{r}
RTB_21C_List<-list()  
Output_Milk_RTB_21C<-LMO_Function_Single_Milk(Cont = 0, Pop_Max =8.5, Time_Temp_df = Df_RT_MT_RTB_21C, Interval =1/60,AF = 1)
Changes_Over_Time_RTB_21C<-Output_Milk_RTB_21C[[2]]
for (i in 1:50){
  AnalysysDF_RTB_21C<- Appling_Changes(df = Outs_DFs_RTB_21C[[i]], Changes_Over_Time = Changes_Over_Time_RTB_21C)
  RTB_21C_List<-append(RTB_21C_List,list(AnalysysDF_RTB_21C))
}


RTB_21C_List[[i]]

RTB_21C_Combined <- bind_rows(RTB_21C_List)
```



##23C
```{r}
RTB_23C_List<-list()  
Output_Milk_RTB_23C<-LMO_Function_Single_Milk(Cont = 0, Pop_Max =8.5, Time_Temp_df = Df_RT_MT_RTB_23C, Interval =1/60,AF = 1)
Changes_Over_Time_RTB_23C<-Output_Milk_RTB_23C[[2]]
for (i in 1:50){
  AnalysysDF_RTB_23C<- Appling_Changes(df = Outs_DFs_RTB_23C[[i]], Changes_Over_Time = Changes_Over_Time_RTB_23C)
  RTB_23C_List<-append(RTB_23C_List,list(AnalysysDF_RTB_23C))
}

RTB_23C_List[[i]]

RTB_23C_Combined <- bind_rows(RTB_23C_List)

```



#Refrigeration Temperature Conditions
##ref7C
```{r}
Ref_7C_List<-list()  
Output_Milk_Ref_7C<-LMO_Function_Single_Milk(Cont = 0, Pop_Max =8.5, Time_Temp_df = Df_RT_MT_Ref_7C, Interval =1/60,AF = 1)
Changes_Over_Time_Ref_7C<-Output_Milk_Ref_7C[[2]]
for (i in 1:50){
  AnalysysDF_Ref_7C<- Appling_Changes(df = Outs_DFs_Ref_7C[[i]], Changes_Over_Time = Changes_Over_Time_Ref_7C)
  Ref_7C_List<-append(Ref_7C_List,list(AnalysysDF_Ref_7C))
}

Ref_7C_List[[i]]

Ref_7C_Combined <- bind_rows(Ref_7C_List)

```

##ref4C
```{r}
Ref_4C_List<-list()  
Output_Milk_Ref_4C<-LMO_Function_Single_Milk(Cont = 0, Pop_Max =8.5, Time_Temp_df = Df_RT_MT_Ref_4C, Interval =1/60,AF = 1)
Changes_Over_Time_Ref_4C<-Output_Milk_Ref_4C[[2]]
for (i in 1:50){
  AnalysysDF_Ref_4C<- Appling_Changes(df = Outs_DFs_Ref_4C[[i]], Changes_Over_Time = Changes_Over_Time_Ref_4C)
  Ref_4C_List<-append(Ref_4C_List,list(AnalysysDF_Ref_4C))
}

Ref_4C_List[[i]]

Ref_4C_Combined <- bind_rows(Ref_4C_List)

```


##ref2C
```{r}
Ref_2C_List<-list()  
Output_Milk_Ref_2C<-LMO_Function_Single_Milk(Cont = 0, Pop_Max =8.5, Time_Temp_df = Df_RT_MT_Ref_2C, Interval =1/60,AF = 1)
Changes_Over_Time_Ref_2C<-Output_Milk_Ref_2C[[2]]
for (i in 1:50){
  AnalysysDF_Ref_2C<- Appling_Changes(df = Outs_DFs_Ref_2C[[i]], Changes_Over_Time = Changes_Over_Time_Ref_2C)
  Ref_2C_List<-append(Ref_2C_List,list(AnalysysDF_Ref_2C))
}

Ref_2C_List[[i]]

Ref_2C_Combined <- bind_rows(Ref_2C_List)
```




#Number of Services and Breaks
##s1b0
```{r}
s1b0_List<-list()  
Output_Milk_s1b0<-LMO_Function_Single_Milk(Cont = 0, Pop_Max =8.5, Time_Temp_df = Df_RT_MT_s1b0, Interval =1/60,AF = 1)
Changes_Over_Time_s1b0<-Output_Milk_s1b0[[2]]
for (i in 1:50){
  AnalysysDF_s1b0<- Appling_Changes(df = Outs_DFs_1sb0[[i]], Changes_Over_Time = Changes_Over_Time_s1b0)
  s1b0_List<-append(s1b0_List,list(AnalysysDF_s1b0))
}
s1b0_List[[i]]

s1b0_Combined <- bind_rows(s1b0_List)

```

##s2b1
```{r}
s2b1_List<-list()  
Output_Milk_s2b1<-LMO_Function_Single_Milk(Cont = 0, Pop_Max =8.5, Time_Temp_df = Df_RT_MT_s2b1, Interval =1/60,AF = 1)
Changes_Over_Time_s2b1<-Output_Milk_s2b1[[2]]
for (i in 1:50){
  AnalysysDF_s2b1<- Appling_Changes(df = Outs_DFs_2sb1[[i]], Changes_Over_Time = Changes_Over_Time_s2b1)
  s2b1_List<-append(s2b1_List,list(AnalysysDF_s2b1))
}
s2b1_List[[i]]

s2b1_Combined <- bind_rows(s2b1_List)

```

##s3b2
```{r}
s3b2_List<-list()  
Output_Milk_s3b2<-LMO_Function_Single_Milk(Cont = 0, Pop_Max =8.5, Time_Temp_df = Df_RT_MT_s3b2, Interval =1/60,AF = 1)
Changes_Over_Time_s3b2<-Output_Milk_s3b2[[2]]
for (i in 1:50){
  AnalysysDF_s3b2<- Appling_Changes(df = Outs_DFs_3sb2[[i]], Changes_Over_Time = Changes_Over_Time_s3b2)
  s3b2_List<-append(s3b2_List,list(AnalysysDF_s3b2))
}
s3b2_List[[i]]

s3b2_Combined <- bind_rows(s3b2_List)

```


##s4b3
```{r}
s43b_List<-list()  
Output_Milk_s43b<-LMO_Function_Single_Milk(Cont = 0, Pop_Max =8.5, Time_Temp_df = Df_RT_MT_s4b3, Interval =1/60,AF = 1)
Changes_Over_Time_s43b<-Output_Milk_s43b[[2]]
for (i in 1:50){
  AnalysysDF_s43b<- Appling_Changes(df = Outs_DFs_4s3b[[i]], Changes_Over_Time = Changes_Over_Time_s43b)
  s43b_List<-append(s43b_List,list(AnalysysDF_s43b))
}
s43b_List[[i]]

s4b3_Combined <- bind_rows(s43b_List)

```

##s4b3TIC
```{r}
s43b_ListTIC<-list()  
Output_Milk_s43b<-LMO_Function_Single_Milk(Cont = 0, Pop_Max =8.5, Time_Temp_df = Df_RT_MT_s4b3TIC, Interval =1/60,AF = 1)
Changes_Over_Time_s43b<-Output_Milk_s43b[[2]]
for (i in 1:50){
  AnalysysDF_s43b<- Appling_Changes(df = Outs_DFs_4s3b[[i]], Changes_Over_Time = Changes_Over_Time_s43b)
  s43b_ListTIC<-append(s43b_ListTIC,list(AnalysysDF_s43b))
}
s43b_List[[i]]

s4b3TIC_Combined <- bind_rows(s43b_ListTIC)

```

##s4b3TIP
```{r}
s43bTIP_List<-list()  
Output_Milk_s43b<-LMO_Function_Single_Milk(Cont = 0, Pop_Max =8.5, Time_Temp_df = Df_RT_MT_s4b3TIP, Interval =1/60,AF = 1)
Changes_Over_Time_s43b<-Output_Milk_s43b[[2]]
for (i in 1:50){
  AnalysysDF_s43b<- Appling_Changes(df = Outs_DFs_4s3b[[i]], Changes_Over_Time = Changes_Over_Time_s43b)
  s43bTIP_List<-append(s43bTIP_List,list(AnalysysDF_s43b))
}

s43b_List[[i]]

s4b3TIP_Combined <- bind_rows(s43bTIP_List)

```



##s5b4
```{r}
s54b_List<-list()  
Output_Milk_s54b<-LMO_Function_Single_Milk(Cont = 2.44, Pop_Max =8.14, Time_Temp_df = Df_RT_MT_s5b4, Interval =1/60,AF = 1.32)
Changes_Over_Time_s54b<-Output_Milk_s54b[[2]]
for (i in 1:50){
  AnalysysDF_s54b<- Appling_Changes(df = Outs_DFs_5s4b[[i]], Changes_Over_Time = Changes_Over_Time_s54b)
  s54b_List<-append(s54b_List,list(AnalysysDF_s54b))
}

s54b_List[[i]]

s5b4_Combined <- bind_rows(s54b_List)


```

##s5b4TIC
```{r}
s54bTIC_List<-list()  
Output_Milk_s54b<-LMO_Function_Single_Milk(Cont = 2.44, Pop_Max =8.14, Time_Temp_df = Df_RT_MT_s5b4TIC, Interval =1/60,AF = 1.32)
Changes_Over_Time_s54b<-Output_Milk_s54b[[2]]
for (i in 1:50){
  AnalysysDF_s54b<- Appling_Changes(df = Outs_DFs_5s4b[[i]], Changes_Over_Time = Changes_Over_Time_s54b)
  s54bTIC_List<-append(s54bTIC_List,list(AnalysysDF_s54b))
}

s54bTIC_List[[i]]

s5b4TIC_Combined <- bind_rows(s54bTIC_List)


```

##s5b4TIP
```{r}
s54bTIP_List<-list()  
Output_Milk_s54b<-LMO_Function_Single_Milk(Cont = 0, Pop_Max =8.5, Time_Temp_df = Df_RT_MT_s5b4TIP, Interval =1/60,AF = 1)
Changes_Over_Time_s54b<-Output_Milk_s54b[[2]]
for (i in 1:50){
  AnalysysDF_s54b<- Appling_Changes(df = Outs_DFs_5s4b[[i]], Changes_Over_Time = Changes_Over_Time_s54b)
  s54bTIP_List<-append(s54bTIP_List,list(AnalysysDF_s54b))
}

s54bTIP_List[[i]]

s5b4TIP_Combined <- bind_rows(s54bTIP_List)

```



#No Share table
##No_ST
```{r}
SToff_List<-list()  
Output_Milk_SToff<-LMO_Function_Single_Milk(Cont = 0, Pop_Max =8.5, Time_Temp_df = Df_RT_MT_RTB, Interval =1/60,AF = 1)
Changes_Over_Time_SToff<-Output_Milk_SToff[[2]]

for (i in 1:50){
  AnalysysDF_SToff<- Appling_Changes(df = Outs_DFs_SToff[[i]], Changes_Over_Time = Changes_Over_Time_SToff)
  SToff_List<-append(SToff_List,list(AnalysysDF_SToff))
}

SToff_List[[i]]

SToff_Combined <- bind_rows(SToff_List)
```


# Output the RDS dataset 
```{r}
saveRDS(RTB_Combined, file = "Output Data/RTB.rds")
saveRDS(RT_Combined, file = "Output Data/RT.rds")
saveRDS(TIP_Combined, file = "Output Data/TIP.rds")
saveRDS(TIC_Combined, file = "Output Data/TIC.rds")
saveRDS(CI_Combined, file = "Output Data/CI.rds")
saveRDS(RTB_refB_Combined, file = "Output Data/RTB_refB.rds")
saveRDS(RTB_18C_Combined, file = "Output Data/RTB_18C.rds")
saveRDS(RTB_21C_Combined, file = "Output Data/RTB_21C.rds")
saveRDS(RTB_23C_Combined, file = "Output Data/RTB_23C.rds")
saveRDS(Ref_2C_Combined, file = "Output Data/Ref_2C.rds")
saveRDS(Ref_4C_Combined, file = "Output Data/Ref_4C.rds")
saveRDS(Ref_7C_Combined, file = "Output Data/Ref_7C.rds")
saveRDS(SToff_Combined, file="Output Data/SToff.rds")

saveRDS(s1b0_Combined, file = "Output Data/s1b0.rds")
saveRDS(s2b1_Combined, file = "Output Data/s2b1.rds")
saveRDS(s3b2_Combined, file = "Output Data/s3b2.rds")
saveRDS(s4b3_Combined, file = "Output Data/s4b3.rds")
saveRDS(s5b4_Combined, file = "Output Data/s5b4.rds")

saveRDS(s4b3TIC_Combined, file = "Output Data/s4b3TIC.rds")
saveRDS(s4b3TIP_Combined, file = "Output Data/s4b3TIP.rds")
saveRDS(s5b4TIC_Combined, file = "Output Data/s5b4TIC.rds")
saveRDS(s5b4TIP_Combined, file = "Output Data/s5b4TIP.rds")

saveRDS(RTB_highcon_Combined, file = "Output Data/RTB_highcon.rds")
```

# Load the Analysis dataset
```{r}
AnalysysDF_RTB <- readRDS("Input Data/RTB.rds")
AnalysysDF_RT <- readRDS("Input Data/RT.rds")
AnalysysDF_TIP <- readRDS("Input Data/TIP.rds")
AnalysysDF_TIC <- readRDS("Input Data/TIC.rds")
AnalysysDF_CI <- readRDS("Input Data/CI.rds")
AnalysysDF_RTB_refB <- readRDS("Input Data/RTB_refB.rds")
AnalysysDF_RTB_18C <- readRDS("Input Data/RTB_18C.rds")
AnalysysDF_RTB_21C <- readRDS("Input Data/RTB_21C.rds")
AnalysysDF_RTB_23C <- readRDS("Input Data/RTB_23C.rds")
AnalysysDF_Ref_2C <- readRDS("Input Data/Ref_2C.rds")
AnalysysDF_Ref_4C <- readRDS("Input Data/Ref_4C.rds")
AnalysysDF_Ref_7C <- readRDS("Input Data/Ref_7C.rds")
AnalysysDF_SToff <- readRDS("Input Data/SToff.rds")

AnalysysDF_s1b0 <- readRDS("Input Data/s1b0.rds")
AnalysysDF_s2b1 <- readRDS("Input Data/s2b1.rds")
AnalysysDF_s3b2 <- readRDS("Input Data/s3b2.rds")
AnalysysDF_s4b3 <- readRDS("Input Data/s4b3.rds")
AnalysysDF_s5b4 <- readRDS("Input Data/s5b4.rds")

AnalysysDF_s4b3TIC <- readRDS("Input Data/s4b3TIC.rds")
AnalysysDF_s4b3TIP <- readRDS("Input Data/s4b3TIP.rds")
AnalysysDF_s5b4TIC <- readRDS("Input Data/s5b4TIC.rds")
AnalysysDF_s5b4TIP <- readRDS("Input Data/s5b4TIP.rds")

AnalysysDF_RTB_highcon <- readRDS("Input Data/RTB_highcon.rds")
```


##Start of the Milk Analysis based on main output dataframe for Pinto 2025 study
# Dose response test for listeria 
```{r}
library(dplyr)
### Create a list for looping the DR analysis for 22 scenarios
AnalysysDF_list<- c("AnalysysDF_RTB", "AnalysysDF_RT", "AnalysysDF_TIP", "AnalysysDF_TIC", 
                    "AnalysysDF_CI", "AnalysysDF_RTB_refB", "AnalysysDF_RTB_18C", 
                    "AnalysysDF_RTB_21C", "AnalysysDF_RTB_23C",
                    "AnalysysDF_Ref_2C","AnalysysDF_Ref_4C","AnalysysDF_Ref_7C", 
                    "AnalysysDF_s1b0", "AnalysysDF_s2b1","AnalysysDF_s3b2", 
                    "AnalysysDF_s4b3","AnalysysDF_s5b4","AnalysysDF_s4b3TIC", 
                    "AnalysysDF_s4b3TIP","AnalysysDF_s5b4TIC","AnalysysDF_s5b4TIP",
                    "AnalysysDF_SToff", "AnalysysDF_RTB_highcon")


for (i in 1:23) {
  Analysys_DR <- get(AnalysysDF_list[i]) %>% 
  filter(Location == "Consumed") %>% 
  dplyr::select(ID, Location, LMOCon, Shared)
  
  assign(paste0("DR_",AnalysysDF_list[i]), Analysys_DR)
}

### dose response function: exponential model with r randomly draw from lognormal distribution
dose_response_listeria <- function(df, r_mean, r_sd, serving_size, scenario) {
  set.seed(12345)
  r <- 10^(rnorm(nrow(df), r_mean, r_sd)) 
  
  dose <- 10^(df$LMOCon) * serving_size
  df$p_ill <- 1 - exp(-r * dose)
  
  result <- data.frame(scenario = scenario,
                       mean_pill = mean(df$p_ill, na.rm = TRUE))
  return(result)
}

### Run DR for 23 scenario and get Pill mean using for loop 
DR_AnalysysDF_list <- paste0("DR_", AnalysysDF_list)
DR_result<- list()

for (i in 1:23) {
  DR_result[[i]]<-dose_response_listeria(get(DR_AnalysysDF_list[i]), 
                                         r_mean = -12.582, r_sd = 0.836, 
                                         serving_size = 236, AnalysysDF_list[i])
  
}
DR_result_conbimed <- do.call(rbind, DR_result)
DR_result_conbimed
DR_result_conbimed$n_trials <- c(
  714578, 714578, 714578, 714578, 714578, 714578,
  714578, 714578, 714578, 714578, 714578, 714578,
  623994, 355019, 714443, 1074910, 1434626, 1794887,
  1434626, 1434626, 1794887, 1794887, 714716)
DR_result_conbimed$ill_1_school <- DR_result_conbimed$mean_pill * DR_result_conbimed$n_trials/50

DR_result_conbimed$pr_yr_all <- DR_result_conbimed$ill_1_school*98577
DR_result_conbimed$ year_mean <- 1/DR_result_conbimed$pr_yr_all
DR_result_conbimed

### output the excel
writexl::write_xlsx(DR_result_conbimed, path = "Output Data/DR_Output_for_23_Scenarios.xlsx")

```

```{r}
#Apply to all scenarios to calculate the uncertainty of the t_case

#Calculate percentiles from binomial distribution and convert to years until 1 illness observed
year_limits = DR_result_conbimed %>%
  group_by(scenario)%>%
  summarise(
    lower_ci = qpois(p = 0.05, lambda = (pr_yr_all*n_trials), lower.tail = FALSE),
    median = qpois(p = 0.50, lambda = (pr_yr_all*n_trials), lower.tail = FALSE),
    mean_years = round(1/(pr_yr_all),0),
    upper_ci = qpois(p = 0.95, lambda = (pr_yr_all*n_trials), lower.tail = FALSE),
    lower_years = round(1/(lower_ci/n_trials),0),
    median_years = round(1/(median/n_trials),0),
    upper_years = round(1/(upper_ci/n_trials),0)
  )%>%
  ungroup()%>%
  select(scenario, lower_years, median_years, mean_years, upper_years)

### output the excel
writexl::write_xlsx(year_limits, path = "Output Data/DR_Output_for_23_Scenarios_t_case.xlsx")
```

#### Exact time for Listeria in milk to reach 1 log increase
```{r}
## Function calculate the time for Listeria growth reach 1 log 
LMO_for_1log_change<-function(Cont, Pop_Max, Time_Temp_df, Interval =1/60, AF, scenario){
  Lag_Consumed = 0
  Output_Milk<-Func_Growth_LagCon(In_Lag_Consumed = Lag_Consumed ,Time_Temp_df = Time_Temp_df,Interval = Interval, AF=AF)
  Lag_Consumed = Output_Milk[[2]]
  Cont<-Output_Milk[[1]]+Cont
  if( Cont>Pop_Max){
     Cont = Pop_Max
  }
  Time_1log_change <- ifelse(length(which(Output_Milk[[3]] >= 1)) > 0, which(Output_Milk[[3]] >= 1)[1], NA)
  Time_1log_change <-Time_1log_change/60/24
  results <- data.frame(scenario = scenario,
                       Time = Time_1log_change)
  return (results)
}

### Create a list for looping the Listeria time and temperature profile for 22 scenarios
DF_RT_list<- c("Df_RT_MT_RTB", "Df_RT_MT_RT", "Df_RT_MT_TIP", "Df_RT_MT_TIC", 
                  "Df_RT_MT_CI", "Df_RT_MT_RTB_refB", "Df_RT_MT_RTB_18C", "Df_RT_MT_RTB_21C", 
                  "Df_RT_MT_RTB_23C","Df_RT_MT_Ref_2C", "Df_RT_MT_Ref_4C", "Df_RT_MT_Ref_7C",
                  "Df_RT_MT_s1b0", "Df_RT_MT_s2b1", "Df_RT_MT_s3b2", "Df_RT_MT_s4b3","Df_RT_MT_s5b4", 
                  "Df_RT_MT_s4b3TIC", "Df_RT_MT_s4b3TIP", "Df_RT_MT_s5b4TIC", "Df_RT_MT_s5b4TIP", "Df_RT_MT_RTB", "Df_RT_MT_RTB")

Time_1log_result<- list()
for (i in 1:23) {
  Time_1log_result[[i]] <- LMO_for_1log_change(Cont = 0, Pop_Max =8.5, Time_Temp_df = get(DF_RT_list[i]), Interval =1/60,AF = 1, DF_RT_list[i])
  
}
Time_1log_result_conbimed <- do.call(rbind, Time_1log_result)

Time_1log_result_conbimed


##### output the excel
writexl::write_xlsx(Time_1log_result_conbimed, path = "Output Data/Time_to_1log_23_Scenarios.xlsx")
```



#### Categorical analysis for percentage of consumed milks over 1log change in service days
```{r}
library(dplyr)
# Function for catergorical analysis for consumed milks reach 1 log change for different service time
Cat_Time_1log = function(df, bell_schedule){
  df$log_change = df$LMOCon - df$InLMOCon
  df$log_1_change = ifelse(df$log_change >= 1, df$log_change, 0)
  df$lunch_sched = ifelse(df$TotTime >= 0 & df$TotTime <= bell_schedule, "Day 1",
                                ifelse(df$TotTime > bell_schedule & df$TotTime <= bell_schedule+1440, "Day 2",
                                ifelse(df$TotTime > bell_schedule+1440 & df$TotTime <=bell_schedule+1440*2, "Day 3",
                                ifelse(df$TotTime >bell_schedule+1440*2 & df$TotTime <=bell_schedule+1440*3, "Day 4","Day 5"))))
  output = df %>%
    dplyr::select(lunch_sched, Location, log_1_change, log_change) %>%
    filter(Location == "Consumed") %>%
    group_by(lunch_sched) %>%
    dplyr::summarize(
      milks_consumed = n(),
      milks_consumed_1_log = sum(log_1_change >= 1),
      max_log_change_per_day = round(max(log_change), 2))%>%
    mutate(prevalence_pct = round((milks_consumed_1_log / milks_consumed) * 100, 4))
  return(output)
}

# Run the function to 23 scenarios 
Cat_Time_1log(AnalysysDF_RTB,125)
Cat_Time_1log(AnalysysDF_RT,125)
Cat_Time_1log(AnalysysDF_TIP,125)
Cat_Time_1log(AnalysysDF_TIC,125)
Cat_Time_1log(AnalysysDF_CI,125)
Cat_Time_1log(AnalysysDF_RTB_refB,125)
Cat_Time_1log(AnalysysDF_RTB_18C,125)
Cat_Time_1log(AnalysysDF_RTB_21C,125)
Cat_Time_1log(AnalysysDF_RTB_23C,125)
Cat_Time_1log(AnalysysDF_Ref_2C,125)
Cat_Time_1log(AnalysysDF_Ref_4C,125)
Cat_Time_1log(AnalysysDF_Ref_7C,125)


Cat_Time_1log(AnalysysDF_s1b0,40)
Cat_Time_1log(AnalysysDF_s2b1,74)
Cat_Time_1log(AnalysysDF_s3b2,125)
Cat_Time_1log(AnalysysDF_s4b3,221)
Cat_Time_1log(AnalysysDF_s5b4,266)

Cat_Time_1log(AnalysysDF_s4b3TIC,221)
Cat_Time_1log(AnalysysDF_s4b3TIP,221)
Cat_Time_1log(AnalysysDF_s5b4TIC,266)
Cat_Time_1log(AnalysysDF_s5b4TIP,266)

Cat_Time_1log(AnalysysDF_SToff,125)

Cat_Time_1log(AnalysysDF_RTB_highcon,125)
```

## Listeria concentration at consumption 
```{r}
library(dplyr)

#function for obtaining summary stats

summary_stats_lm = function(df){
  summary_stats = df %>%
    filter(Location == "Consumed")%>%
    ungroup()%>%
    dplyr::summarize(
      min_lm = round(min(LMOCon, na.rm = TRUE),2),
      mean_lm = round(mean(LMOCon, na.rm = TRUE),2),
      median_lm = round(median(LMOCon, na.rm = TRUE),2),
      maximum_lm = round(max(LMOCon, na.rm = TRUE),2),
      fifthpct_lm = round(quantile(LMOCon, 0.05, na.rm = TRUE),2),
      nfpct_lm = round(quantile(LMOCon, 0.95, na.rm = TRUE),2)
    )
}

#combining into list so I can use lapply
df_list = list(AnalysysDF_RTB = AnalysysDF_RTB, 
  AnalysysDF_SToff = AnalysysDF_SToff, 
  AnalysysDF_RT = AnalysysDF_RT, 
  AnalysysDF_TIP = AnalysysDF_TIP, 
  AnalysysDF_TIC = AnalysysDF_TIC, 
  AnalysysDF_CI = AnalysysDF_CI, 
  AnalysysDF_RTB_refB = AnalysysDF_RTB_refB, 
  AnalysysDF_Ref_2C = AnalysysDF_Ref_2C, 
  AnalysysDF_Ref_4C = AnalysysDF_Ref_4C, 
  AnalysysDF_Ref_7C = AnalysysDF_Ref_7C, 
  AnalysysDF_RTB_18C = AnalysysDF_RTB_18C, 
  AnalysysDF_RTB_21C = AnalysysDF_RTB_21C, 
  AnalysysDF_RTB_23C = AnalysysDF_RTB_23C, 
  AnalysysDF_s1b0 = AnalysysDF_s1b0, 
  AnalysysDF_s2b1 = AnalysysDF_s2b1, 
  AnalysysDF_s3b2 = AnalysysDF_s3b2, 
  AnalysysDF_s4b3 = AnalysysDF_s4b3, 
  AnalysysDF_s5b4 = AnalysysDF_s5b4, 
  AnalysysDF_s4b3TIC = AnalysysDF_s4b3TIC, 
  AnalysysDF_s4b3TIP = AnalysysDF_s4b3TIP, 
  AnalysysDF_s5b4TIC = AnalysysDF_s5b4TIC, 
  AnalysysDF_s5b4TIP = AnalysysDF_s5b4TIP, 
  AnalysysDF_RTB_highcon = AnalysysDF_RTB_highcon
  )

library(purrr)
df_list_with_names <- lapply(names(df_list), function(df_name) {
  df <- df_list[[df_name]]
  df$data_frame_name <- df_name
  return(df)
})

final_summary_stats <- bind_rows(lapply(df_list_with_names, function(df) {
  summary_stats <- summary_stats_lm(df)  # Apply summary stats
  summary_stats$data_frame_name <- df$data_frame_name[1]  # Add the data frame name
  return(summary_stats)
}))

final_summary_stats

library(writexl)
write_xlsx(final_summary_stats, "Output Data/final_LMOCon_stats.xlsx")
```


## Calculate the L. monocytogenes growth in Day 1 + create comparison box plot
```{r}
# change during first service - baseline and no ST

delta_d1 = function(df, bell_schedule){
  output = df %>%
    mutate(
      log_change = LMOCon - InLMOCon,
    ) %>%
    dplyr::select(Location, log_change, TotTime) %>%
    filter(TotTime >= 0 & TotTime <= bell_schedule)%>%
    group_by(Location) %>%
    dplyr::summarize(
      median_change = median(log_change),
      mean_change = mean(log_change),
      sd_change = sd(log_change),
      median_time = median(TotTime),
      mean_time = mean(TotTime),
      sd_time = sd(TotTime)
      )
  return(output)
}

d1_rtb = delta_d1(AnalysysDF_RTB, 125)
d1_stoff = delta_d1(AnalysysDF_SToff, 125)

d1_change = rbind(d1_rtb, d1_stoff)

##### output the excel
writexl::write_xlsx(d1_change, path = "Output Data/Growth_during_d1.xlsx")

# Extract the data for figure  
output_rtb = AnalysysDF_RTB %>%
    mutate(
      log_change = LMOCon - InLMOCon,
    ) %>%
    select(Location, log_change, TotTime) %>%
    filter(TotTime >= 0 & TotTime <= 125)%>%
    group_by(Location)

output_rtb$scenario = "Baseline"

output_stoff = AnalysysDF_SToff %>%
    mutate(
      log_change = LMOCon - InLMOCon,
    ) %>%
    select(Location, log_change, TotTime) %>%
    filter(TotTime >= 0 & TotTime <= 125)%>%
    group_by(Location)
output_stoff$scenario = "Share Table Off"

bound_delta_d1 = rbind(output_rtb, output_stoff)
bound_delta_d1$scenario <- as.factor(bound_delta_d1$scenario)

custom_box_data <- bound_delta_d1 %>%
  group_by(scenario, Location) %>%
  summarise(
    fifth = quantile(log_change, 0.05),
    lower = quantile(log_change, 0.25),
    middle = quantile(log_change, 0.50),
    upper = quantile(log_change, 0.75),
    ninfith = quantile(log_change, 0.95),
    .groups = 'drop'
  )

### create the box plot for comparison
ggplot(custom_box_data, aes(x = scenario, fill = scenario)) +
  geom_boxplot(aes(
      ymin = fifth,
      lower = lower,
      middle = middle,
      upper = upper,
      ymax = ninfith),
      stat = "identity",
      width = 0.5)+
  scale_fill_manual(values = c("#D3D3D3", "#666666"))+ 
  facet_wrap(~Location, drop = TRUE)+
  labs(
    x = "",
    y = expression("Log"["10"]*" Change of "*italic("L. monocytogenes")*
                     "During First Day of Services (Log"["10"]*" CFU/ml)"),
    fill = "Scenario")+
  theme_minimal() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.x = element_text(angle = 45, hjust = 1, color = "black", size =14),
    axis.text.y = element_text(color = "black", size = 14),
    axis.title.y = element_text(size = 12),
    strip.background = element_rect(color = "black", fill = "white", linewidth = 1),
    strip.text = element_text(color = "black", size = 16),
    axis.line = element_line(color = "black", linewidth = 0.5),
    legend.position = "none"
    )

### save the graph 
ggsave("Figures/boxplot_d1.jpg", 
       plot = last_plot(),
       dpi = 600,             
       width = 10,            
       height = 8,           
       units = "in",          
       device = "jpg")
```

